Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-03-04 Paper.tex
Corrected constant coefficient of G2
Fix Elliptic Curve group addition equations

\hypertarget{block_gas_limit_H__l}{}The canonical gas limit $H_{\mathrm{l}}$ of a block of header $H$ must fulfil the relation:
\begin{eqnarray}
& & H_{\mathrm{l}} < {P(H)_{H}}_{\mathrm{l}} + \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor \quad \wedge \\
\nonumber& & H_{\mathrm{l}} > {P(H)_{H}}_{\mathrm{l}} - \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor \quad \wedge \\
\nonumber& & H_{\mathrm{l}} \geqslant 5000
\end{eqnarray}

@@

\hypertarget{block_header_validity_function}{}Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv &  n \leqslant \frac{2^{256}}{H_{\mathrm{d}}} \wedge m = H_{\mathrm{m}} \quad \wedge \\
\nonumber & & H_{\mathrm{d}} = D(H) \quad \wedge \\
\nonumber& & H_{\mathrm{g}} \le H_{\mathrm{l}}  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} < {P(H)_{H}}_{\mathrm{l}} + \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} > {P(H)_{H}}_{\mathrm{l}} - \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} \geqslant 5000  \quad \wedge \\
\nonumber& & H_{\mathrm{s}} > {P(H)_{H}}_{\mathrm{s}} \quad \wedge \\
\nonumber& & H_{\mathrm{i}} = {P(H)_{H}}_{\mathrm{i}} +1 \quad \wedge \\
\nonumber& & \lVert H_{\mathrm{x}} \rVert \le 32
\end{eqnarray}
where $(n, m) = \mathtt{PoW}(H_{\hcancel{n}}, H_{\mathrm{n}}, \mathbf{d})$

@@

We define a set~$C_1$ with
\begin{equation}
C_1\equiv\{(X,Y)\in F_{\mathrm{p}}\times F_{\mathrm{p}}\mid Y^2=X^3+3\}\cup\{(0,0)\}
\end{equation}
We define a binary operation $+$ on $C_1$ with
\begin{eqnarray}\label{eq:ec-addition}
(X_1, Y_1) + (X_2, Y_2)&\equiv&\begin{cases}
(X,Y)&\text{if}\ X_1\neq X_2\\
(0,0)&\text{otherwise}
\end{cases}\\
X&\equiv&\lambda^2-X_1-X_2\\
Y&\equiv&\lambda(X_1-X)-Y_1\\
\lambda&\equiv&\frac{Y_2-Y_1}{X_2-X_1}
\end{eqnarray}

@@

Let $F_{p^2}$ be a field $F_{\mathrm{p}}[i]/(i+1)$. We define a set $C_2$ with
\begin{equation}
C_2\equiv\{(X,Y)\in F_{p^2}\times F_{p^2}\mid Y^2=X^3+3\}\cup\{(0,0)\}
\end{equation}
We define a binary operation $+$ and a scalar multiplication $\cdot$ with the same equations (\ref{eq:ec-addition}) and (\ref{eq:ec-scalar-multiplication}). $(C_2,+)$ is also known to be a group. We define $P_2$ in $C_2$ with
\begin{eqnarray}
P_2&\equiv&
(11559732032986387107991004021392285783925812861821192530917403151452391805634 \times i\\\nonumber &&+ 10857046999023057135944570762232829481370756359578518086990519993285655852781,\\\nonumber && 4082367875863433681332203403145435568316851327593401208105741076214120093531 \times i\\\nonumber &&+ 8495653923123431417604973247489272438418190587263600148770280649306958101930)
\end{eqnarray}
We define $G_2$ to be the subgroup of $(C_2,+)$ generated by $P_2$. $G_2$ is known to be a cyclic group of order $q$. For a point $P$ in $G_2$, we define $\log_{P_2}(P)$ be the smallest natural number $n$ satisfying $n\cdot P_2=P$. With this definition, $\log_{P_2}(P)$ is at most $q-1$.

>>>>

\hypertarget{block_gas_limit_H__l}{}The canonical gas limit $H_{\mathrm{l}}$ of a block of header $H$ must fulfil the relation:
\begin{eqnarray}
& & H_{\mathrm{l}} < {P(H)_{H}}_{\mathrm{l}} + \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor \quad \wedge \\
& & H_{\mathrm{l}} > {P(H)_{H}}_{\mathrm{l}} - \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor \quad \wedge \\
& & H_{\mathrm{l}} \geqslant 5000
\end{eqnarray}

@@

\hypertarget{block_header_validity_function}{}Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv &  n \leqslant \frac{2^{256}}{H_{\mathrm{d}}} \wedge m = H_{\mathrm{m}} \quad \wedge \\
& & H_{\mathrm{d}} = D(H) \quad \wedge \\
& & H_{\mathrm{g}} \le H_{\mathrm{l}}  \quad \wedge \\
& & H_{\mathrm{l}} < {P(H)_{H}}_{\mathrm{l}} + \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor  \quad \wedge \\
& & H_{\mathrm{l}} > {P(H)_{H}}_{\mathrm{l}} - \left\lfloor\frac{{P(H)_{H}}_{\mathrm{l}}}{1024}\right\rfloor  \quad \wedge \\
& & H_{\mathrm{l}} \geqslant 5000  \quad \wedge \\
& & H_{\mathrm{s}} > {P(H)_{H}}_{\mathrm{s}} \quad \wedge \\
& & H_{\mathrm{i}} = {P(H)_{H}}_{\mathrm{i}} +1 \quad \wedge \\
& & \lVert H_{\mathrm{x}} \rVert \le 32
\end{eqnarray}
where $(n, m) = \mathtt{PoW}(H_{\hcancel{n}}, H_{\mathrm{n}}, \mathbf{d})$

@@

We define a set~$C_1$ with
\begin{equation}
C_1\equiv\{(X,Y)\in F_{\mathrm{p}}\times F_{\mathrm{p}}\mid Y^2=X^3+3\}\cup\{(0,0)\}
\end{equation}
We define a binary operation $+$ on $C_1$ for distinct elements $(X_1, Y_1), (X_2, Y_2)$ with
\begin{eqnarray}\label{eq:ec-addition}
(X_1, Y_1) + (X_2, Y_2)&\equiv&\begin{cases}
(X,Y)&\text{if}\ X_1\neq X_2\\
(0,0)&\text{otherwise}
\end{cases}\\
\lambda&\equiv&\frac{Y_2-Y_1}{X_2-X_1}\\
X&\equiv&\lambda^2-X_1-X_2\\
Y&\equiv&\lambda(X_1-X)-Y_1
\end{eqnarray}

In the case where $(X_1, Y_1) = (X_2, Y_2)$, we define $+$ on $C_1$ with
\begin{eqnarray}\label{eq:ec-doubling}
(X_1, Y_1) + (X_1, Y_1)&\equiv&\begin{cases}
(X,Y)&\text{if}\ Y_1\neq 0\\
(0,0)&\text{otherwise}
\end{cases}\\
\lambda&\equiv&\frac{3X_1^2}{2Y_1}\\
X&\equiv&\lambda^2-2X_1\\
Y&\equiv&\lambda(X_1-X)-Y_1
\end{eqnarray}

@@

Let $F_{p^2}$ be a field $F_{\mathrm{p}}[i]/(i+1)$. We define a set $C_2$ with
\begin{equation}
C_2\equiv\{(X,Y)\in F_{p^2}\times F_{p^2}\mid Y^2=X^3+3\}\cup\{(0,0)\}
\end{equation}
We define a binary operation $+$ and a scalar multiplication $\cdot$ with the same equations (\ref{eq:ec-addition}), (\ref{eq:ec-doubling}) and (\ref{eq:ec-scalar-multiplication}). $(C_2,+)$ is also known to be a group. We define $P_2$ in $C_2$ with
\begin{eqnarray}
P_2&\equiv&
(11559732032986387107991004021392285783925812861821192530917403151452391805634 \times i\\\nonumber &&+ 10857046999023057135944570762232829481370756359578518086990519993285655852781,\\\nonumber && 4082367875863433681332203403145435568316851327593401208105741076214120093531 \times i\\\nonumber &&+ 8495653923123431417604973247489272438418190587263600148770280649306958101930)
\end{eqnarray}
We define $G_2$ to be the subgroup of $(C_2,+)$ generated by $P_2$. $G_2$ is known to be a cyclic group of order $q$. For a point $P$ in $G_2$, we define $\log_{P_2}(P)$ be the smallest natural number $n$ satisfying $n\cdot P_2=P$. With this definition, $\log_{P_2}(P)$ is at most $q-1$.
